Characteristic polynomials of p-adic matrices

### 2017-01-27 charpoly/charpoly.tex
Small reorganization of the paper of char. poly.

\section{Computation of the characteristic polynomial and its derivative}

@@

%\subsection{$\com (X -M)$ and jagged precision}

\subsection{Factorization}

When this time $dM$ is jagged, the trick of the proof of Proposition
\ref{prop:optimal_flat} can not work anymore.
Indeed, the computation of $P^{-1}  dM P$ and then of $\com (X-H) P^{-1}  dM P$
are not easy, as $P^{-1}  dM P$ is not jagged anymore.
Fortunately, a factorization result of $\com (X-M)$ will be enough
to conclude that optimal precision can still be read in $\softO (n^3)$
operations in $O_K.$

@@

Thanks to the previous results, we can now compute 
$\com (X-M) \mod (\chi(M))$ in average complexity $\softO (n^3),$
using the following algorithm.

@@

\section{The case of diagonalizable matrices}

@@

\subsection{Algorithm}

>>>>

\section{Optimal precision\\via Hessenberg form}
%\section{Computation of the characteristic polynomial and its derivative}

@@

@@

When this time $dM$ is jagged, the trick of the proof of Proposition
\ref{prop:optimal_flat} can not work anymore.
Indeed, the computation of $P^{-1}  dM P$ and then of $\com (X-H) P^{-1}  dM P$
are not easy, as $P^{-1}  dM P$ is not jagged anymore.
Fortunately, Proposition~\ref{prop:factom_com} will be enough to 
conclude that optimal precision can still be read in $\softO (n^3)$ 
operations in $O_K.$

%Thanks to the previous results, we can now compute 
%$\com (X-M) \mod (\chi(M))$ in average complexity $\softO (n^3),$
%using the following algorithm.

@@

\section{Optimal precision\\via Frobenius form}

\section{Eigenvalues}

\subsection{Optimal precision on a simple eigenvalue}

\todo{Optimal precision on $P(\lambda_i)$ and on $\lambda_i$}

@@

%\subsection{Algorithm}
